Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-14 paper/paper.tex

\subsection{Seed JS files\label{sec:seeds}}~
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files mined from
issue trackers of these engines, and 4) test files from public engines
accessible from GitHub using the GitHub REST
API~\cite{github-rest-api}.

Table~\ref{tab:test-suites} shows the breakdown of tests we per
source. Column ``original'' shows the number of test cases associated
with each test suite. Column ``pass-in-par.'' shows the number of test
cases that pass in their parent engine. We discarded tests that fail
in their parent engine as we could not reliably indicate the reason
for the failure, so we assumed the test could be broken. We removed 63
test cases that fail for that reason--6 tests from \jsc{} and 57 tests
from \smonkey. Column ``compile-in-all'' shows the number of test
cases whose executions do not throw dynamic type errors in any of the
engines because of an undefined variable or property. We capture these
cases by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc{}'s
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. We used the \totalTestFilesForTestTransplantation{}
tests included in the circle from the table in the evaluation of test
transplantation, \ie{}, all tests under the ``compile-in-all''
column\Mar{change name to type-in-all}
but the Test262 tests. We did not consider tests from the conformance
suite as they are more likely to indicate missing features as opposed
to bugs. In addition, engine developers have access to these test and
are encouraged to run them.  Column ``no-fail-in-all'' shows the tests
for which all engines pass. This test set is used in the evaluation of
differential testing. Note that it is a proper subset of the
``compile-in-all'' test set. The tests from this group are used as
fuzzing seeds. The guarantee that they pass in all engines assures
that, if discrepancies occur, they are related to the changes in the
input as opposed to the original cause of failure.

@@

N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
se um bloco de texto eh um bloco de codigo.

Motivacao:
Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
de similaridade entre elas.
Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
(melhorar definicao do modelo)

Inputs:
Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).

Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.

\Fix{...elaborate...}

\Mar{-------- estou aqui}

@@

>>>>

\subsection{Seed JS files\label{sec:seeds}}~
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files from the suites
of public engines, and 4) test files mined from issue trackers of
these engines.

%% accessible from GitHub using the GitHub REST
%% API~\cite{github-rest-api}.

Table~\ref{tab:test-suites} shows the breakdown of tests we per
engine. Column ``original'' shows the number of test cases associated
with each test suite. Column ``pass-in-par.''  shows the number of
test cases that pass in their parent engine. We discarded tests that
fail in their parent engine as we could not reliably indicate the
reason for the failure, so we assumed the test could be broken. We
removed 63 test cases that fail for that reason--6 tests from \jsc{}
and 57 tests from \smonkey. Column ``compile-in-all'' shows the number
of test cases whose executions do not throw dynamic type errors in any
of the engines because of an undefined variable or property. We
capture these cases by looking for the presence of
\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
when test execution attempts to access an undefined variable
(respectively, property of an object). We discarded those tests to
avoid noise in the experiments as they clearly indicate some missing
feature as opposed to bugs. For example, some tests use non-portable
names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. We used the
\totalTestFilesForTestTransplantation{} tests included in the circle
from the table in the evaluation of test transplantation, \ie{}, all
tests under the ``compile-in-all'' column\Mar{change name to
  type-in-all} but the Test262 tests. We did not consider tests from
the conformance suite as they are more likely to indicate missing
features as opposed to bugs. In addition, engine developers have
access to these test and are encouraged to run them.  Column
``no-fail-in-all'' shows the tests for which all engines pass. This
test set is used in the evaluation of differential testing. Note that
it is a proper subset of the ``compile-in-all'' test set. The tests
from this group are used as fuzzing seeds. The guarantee that they
pass in all engines assures that, if discrepancies occur, they are
related to the changes in the input as opposed to the original cause
of failure.

@@

\sloppy{}We observed that issue trackers are an important source of
test data and should not be ignored. Analyzing a sample of issues, we
observed that developers either 1) add test cases as attachments of
issues or 2) embed test cases within the textual description of an
issue. The test cases in attachments are longer compared to the test
cases embedded in issue descriptions whereas the latter are more
common. Consequently, we thought we should handle both
cases. Accessing attachments is simpler compared to embedded
tests. For attachments, we wrote a crawler to visit the issue trackers
of all four engines listed in Table~\ref{tab:engines} and were able to
retrieve a total of \Fix{XX} files
(\jsc{}=\Fix{XX},\veight{}=\Fix{XX},\chakra{}=\Fix{XX}, and
\smonkey{}=\Fix{XX}). To mine tests from the textual descriptions, we
broke the text describing the issue in paragraphs and used a binary
classifier to label each paragraph as ``code'' or ``not code''. Then,
based on that information, we merged consecutive paragraphs labeled as
``code'' and used a \js\ parser to check well-formedness of the
corresponding code fragment. Using that method we were able to
retrieve a total of \Fix{XX} files
(\jsc{}=\Fix{XX},\veight{}=\Fix{XX},\chakra{}=\Fix{XX}). All those
files were included in Table~\ref{tab:test-suites}.

Surprisingly, we did not find a public classifier to solve the problem
above. For space, we summarize the solution that worked the best in
the following. We used a standard Embeddings NLP
technique~\Fix{cite}\Mar{needs to explain what this ``Embeddings''
  thing does at a high-level. Also, if this stuff exists why we did
  not find a solution off-the-shelf?} that uses a neural
net~\Fix{cite} to keep a dictionary of words and the similarity
distance among them\Mar{but we are talking about sentences. how does
  it go from words to sentences? Note that many words from the
  ``code'' vocabulary are from English!}. In more detail, the
classification model uses a Convolutional Neural Network~\Fix{cite}
classifier with two layers\Mar{why two? is there a meaning for each
  layer?} and has been trained and evaluated using a dataset with 25K
samples of English paragraphs and 25K snippets of \js{}. We ran a
standard \Fix{X}-repeated 10-fold cross validation to evaluate the
model and obtained a predicted accuracy of \Fix{98\%}. This classifier
is publicly available from our website as a separate component.

%% N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
%% Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
%% Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
%% se um bloco de texto eh um bloco de codigo.

%% Motivacao:
%% Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
%% onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
%% de similaridade entre elas.
%% Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
%% Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
%% (melhorar definicao do modelo)

%% Inputs:
%% Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
%% de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
%% Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).

%% Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.

%% \Fix{...elaborate...}

@@

%%  LocalWords:  formedness Embeddings NLP Convolutional dataset
